---
title: "Kaggle - Porn Analysis"
output: html_notebook
---

#Introduction
Pornography has become an inescapable part of our daily lives. We are bombarded with conflicting views of the impact of pornography on society; some argue that it provides a safe means of exploring sexuality (such as sexual orientation, kinks, or potentially risky behavior) while others warn of its potentially addictive nature.
The following Kaggle dataset contains data on 
```{r echo = FALSE, message = FALSE}
library(tidyverse)
```

```{r echo = TRUE, cached = TRUE}
if(!file.exists("./data")){
  fileURL <- "https://www.kaggle.com/ljlr34449/porn-data/downloads/porn-data.zip"
  download.file(url = fileURL, destfile = "./data/porn-data.zip", method = "curl")
}
porn_data <- read_csv("./data/porn-data.zip")
porn_data
```

```{r Exploratory Data Analysis}
summary(porn_data)
str(porn_data)
porn_data <- porn_data %>% 
  mutate(categories = strsplit(categories, split = "__"), tags = strsplit(tags, split = "__"))

```


